Performance of two different ontological and data access methods

### 2014-07-02 cold2014/magnus.tex
classes vs properties
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@708 43ef1190-90fd-4dd7-a769-d0121f02b80e

@@

We will also show how to create a viable web application which
utilizes such complex data, mainly for the purpose of conducting
performance tests to determine the weaknesses of each approach. This
will be done with complex data found on the web today from different
car manufacturers.  With performance we mean the response time between
a HTTP~\cite{http}} post operation against the application and when
the application presents the user with an answer. The application will
contain the possibility to do HTTP posts against both approaches.

>>>>

A central difference with these ontologies is that CO allows the
configuration to be defined in terms of classes, whereas VSO
represents them with properties, for example:
\begin{lstlisting}[basicstyle=\tiny, frame=single]
#CO representation of fuel type
:var_PT1628  a           co:ConfigurationVariable , owl:Class ;
        rdfs:label       "Fuel Type"@en ;
        co:confVarId   "PT1628" ;
        co:hasValue    <http://uk.co.rplug.renault.com/product/gen/spec/PT1628_diesel/-#this> .

#VSO representation of fuel type
daim:A200CDI vso:fuelType daim:A200CDI_fuelType_Diesel_fuel .
\end{lstlisting}

@@

We will also show how to create a viable web application which
utilizes such complex data, mainly for the purpose of conducting
performance tests to determine the weaknesses of each approach. This
will be done with complex data found on the web today from different
car manufacturers.  With performance we mean the response time between
a HTTP post operation against the application and when
the application presents the user with an answer. The application will
contain the possibility to do HTTP posts against both approaches.
